AhirV2: from algorithms to hardware \\ An overview

### 2015-02-07 Documents/AhirV2/AhirV2.tex
Update the Ahir docs with Aa2C related stuff

The options:
\begin{itemize}
\item {\bf -modules=listfile} : Specify the list of functions in the bytecode
which should be converted to \Aa.   The names of these functions should be
listed in the text-file listfile. If absent, all functions
are converted.
\item {\bf -storageinit} :  Storage objects in the llvm bytecode
are explicitly initialized in the generated \Aa code.   An initializer
routine named
\begin{verbatim}
    global_storage_initializer
\end{verbatim}
is instantiated in
the \Aa code for this purpose.
\item {\bf -pipedepths=filename} : Specifies a file which contains
the depths of pipes which are part of the generated \Aa code.
\item {\bf -extract\_do\_while} : Innermost loops which are marked
using a call to the special function 
\begin{verbatim}
    _loop_pipelining_on_
\end{verbatim}
are extracted as pipelined do-while loops.  This is necessary
for automatic parallelization of inner loops in the 
generated hardware (substantial performance benefits can be
realized).
\end{itemize}

@@

>>>>

The options:
\begin{itemize}
\item {\bf -modules=listfile} : Specify the list of functions in the bytecode
which should be converted to \Aa.   The names of these functions should be
listed in the text-file listfile. If absent, all functions
are converted.
\item {\bf -storageinit} :  Storage objects in the llvm bytecode
are explicitly initialized in the generated \Aa code.   An initializer
routine named
\begin{verbatim}
    global_storage_initializer
\end{verbatim}
is instantiated in
the \Aa code for this purpose.
\item {\bf -pipedepths=filename} : Specifies a file which contains
the depths of pipes which are part of the generated \Aa code.
\item {\bf -extract\_do\_while} : Innermost loops which are marked
using a call to the special function 
\begin{verbatim}
    _loop_pipelining_on_
\end{verbatim}
are extracted as pipelined do-while loops.  This is necessary
for automatic cross-iteration parallelization of inner loops in the 
generated hardware (substantial performance benefits can be
realized).
\end{itemize}

@@

\subsection{{\bf Aa2C}: convert an {\bf Aa} description into a {\bf C} program}

The AhirV2 flow offers considerable flexibility to a system designer.
For example, it is possible to write code directly in {\bf Aa} in order
to get more optimal implementations (relative to those obtained 
starting from {\bf C}).  In such cases, if we wish to simulate
the {\bf Aa} description, we would use the {\bf Aa2C} utility to
convert the {\bf Aa} code to ANSI {\bf C}, and then compile it
in the usual way.

The {\bf Aa2C} program can be summarized as
\begin{verbatim}
Aa2C [-I <ext-mem-object>] <aa-file> (<aa-file>)*
\end{verbatim}
The only option is:
\begin{itemize}
\item {\bf -I <ext-mem-object>}:  the same behaviour as in {\bf Aa2VC}.
\end{itemize}
The remaining arguments are {\bf Aa} files which will be linked and
converted to {\bf C} code.  Two outputs files are created:
\begin{itemize}
\item aa\_c\_model.h :  a header file declaring functions in the generated
source code.
\item aa\_c\_model.c : a source file containing function definitions
corresponding to the {\bf Aa} modules.
\end{itemize}

External calls into the generated {\bf C} code must have the
form:
\begin{verbatim}
void foo ( Ctype_1 in_1, Ctype_2 in_2, Ctype_3* out_1, Ctype_4* out_2);
\end{verbatim}
where Ctype is either a float or double or (int/uint)(64/32/16/8)\_t type.
You can then link your external code with the generated {\bf C} code
in the usual way.

\subsubsection{Restrictions in using {\bf Aa2C}}

The current implementation of {\bf Aa2C} produces un-threaded code.
Thus, if you have a parallel block in your {\bf Aa} code, the
statements in the parallel block are serialized in the resulting
{\bf C} program.  This can result in the generated {\bf C} program
potentially hanging (if one of the statements in the parallel
block runs for-ever).   Another situation is when two
concurrent blocks in the {\bf Aa} program are writing and reading
from the same pipe.  In such a case, the serialized code may
get dead-locked.  You need to be careful that your {\bf Aa} code
does not have such situations (the simplest option is
to not use parallel blocks in the {\bf Aa} code!).

This issue will be fixed in a future release of {\bf Aa2C}.
